\chapter{Item Attachments}
Item attachments follow the rules on pages 206--209 of the \emph{Genesys} Core Rulebook. Many of the attachments in that section are available in \emph{Titanfall: Genesys} as well as new attachments described below.

\section{Weapon Attachments}

The following weapon attachments are available to characters in the \emph{Titanfall: Genesys} setting. In addition, several attachments from the \emph{Genesys} Core Rulebook are available.

Italicized attachments are new and found in the following section.


\begin{table}[h!]
\centering
\caption{Weapon Attachments}
\footnotesize
\begin{GenesysTable}{l c r c}
Attachment & HP required & Price & Rarity\\
Bipod Mount & 1 & 250 & 2\\
\emph{Dataspike} & 1 & 500 & 6\\
\emph{Enhanced Targeting Algorithm} & 1 & 800 & 7\\
Extended barrel & 2 & 1,000 & 4\\
Hair Trigger & 1 & 150 & 3\\
\emph{Holosight} & 1 & 500 & 4 \\
\emph{Laser Sight} & 1 & 500 & 5\\
\emph{Silencer} & 1 & 100 & 5\\
Superior Customization & 1 & 750 & 7\\
Telescopic Sight & 1 & 200 & 3\\
Tripod Mount & 2 & 400 & 3\\
Under-barrel Weapon & 2 & Varies & Varies\\
Weapon sling & 1 & 250 & 1\\
\end{GenesysTable}
\end{table}


\subsection{Dataspike}
The Dataspike is a tool used to hack into enemy Spectres, turrets or other computing devices. It has an on-board AI programmed specifically to hack into enemy computers. \\
\noindent\textbf{Use With:} The dataspike is specifically designed to be used with the combat knife.\\
\noindent\textbf{Modifiers:} Dataspikes can perform Hacking checks for a player with a Hacking skill of 2 and an Intellect of 0. If unassisted it rolls \AbilityDie\AbilityDie\ for Hacking checks (see pages 26--27 of the \emph{Genesys} Core Rulebook for rules on assisted checks).\\
\noindent\textbf{Hard Points Required:} 1\\
\noindent\textbf{Price:} 500

\subsection{Enhanced Targeting Algorithm}
While most guided weaponry is good as-is, many users tweak the targeting code to acquire a lock faster.\\
\noindent\textbf{Use With:} Any weapon with the Guided quality may have this attachment.\\
\noindent\textbf{Modifiers:} When you preform the aim manoeuvre you may add \Advantage\ instead of \BoostDie\ to your combat check.\\
\noindent\textbf{Hard Points Required:} 1\\
\noindent\textbf{Price:} 800


\subsection{Holosight}
This device projects a hologram of a crosshair a meter or so in front of the barrel to aid in aiming the weapon. Unfortunately that also makes it easier to spot the shooter.\\
\noindent\textbf{Use With:} Any firearm can have a holosight added.\\
\noindent\textbf{Modifiers:} The shooter may aim as an incidental once per round at a target up to medium range. If the holosight is used, reduce any concealment dice the shooter is benefiting from by 1 until the beginning of the character's next turn (see page 110 of the \emph{Genesys} Core Rulebook for concealment rules).\\
\noindent\textbf{Hard Points Required:} 1\\
\noindent\textbf{Price:} 500

\subsection{Laser Sight}
A simple and lower-tech solution than most on the Frontier are used to, it is a classic for a reason. A laser sight emits a low-level light beam that places a physical dot where the weapon is pointing. But due to the low output it has limited range.\\
\noindent\textbf{Use With:} Any firearm can have a laser sight attached.\\
\noindent\textbf{Modifiers:} A laser sight adds the Accurate 1 quality, or increases an existing Accurate quality by 1.\\
\noindent\textbf{Hard Points Required:}  1\\
\noindent\textbf{Price:} 500

\subsection{Silencer}
A silencer makes it harder for others to pinpoint the location of shots made with the weapon it is attached to.\\
\noindent\textbf{Use With:} Any firearm can have a silencer attached.\\
\noindent\textbf{Modifiers:} Adds \SetbackDie\SetbackDie\ to any Perception or Vigilance checks to locate the shooter firing the weapon.\\
\noindent\textbf{Hard Points Required:}  1\\
\noindent\textbf{Price:} 100


\section{Armour Attachments}

The following armour attachments are available to characters in the \emph{Titanfall: Genesys} setting. In addition, several attachments from the \emph{Genesys} Core Rulebook are available.

Italicized attachments are new and found in the following section.

\begin{table}[h!]
\centering
\caption{Armour Attachments}
\footnotesize
\begin{GenesysTable}{l c r c}
Attachment & HP required & Price & Rarity\\
Deflective Plating & 1 & 450 & 4\\
Enhanced Lifting Servos & 2 & 1,500 & 5\\
\emph{Extra Emitters} & 1 & 2,000 & 6\\
\emph{Extra Padding} & 1 & 300 & 6\\
\emph{Grapple Launcher} & 2 & 350 & 3\\
Reinforced Plating & 2 & 8,000 & 7\\
\emph{Stim Injectors} & 1 & 2,500 & 5\\
Vacuum Sealed & 1 & 600 & 4\\
\end{GenesysTable}
\end{table}





\subsection{Grapple Launcher}
The grapple launcher has a weighted head designed to pierce and hold firm to any solid surface. It allows the wearer to traverse longer distances than normal---even straight up! Whether you're trying to get away, close the distance or get in or out of a secure site in a hurry, the grapple launcher is just what you need. Some crazy pilots even use it to rodeo a Titan!\\
\noindent\textbf{Use With:} This attachment can be applied to any armor.\\
\noindent\textbf{Modifiers:} As an action, a character may make an \textbf{Average (\DifficultyDie\DifficultyDie) Ranged (Light) check} to secure the grapple launcher on any solid object within short range. On a success, they may, as a manoeuvre, reel in the cord and pull themselves towards the the object. If the object is unsecured, it instead is pulled to the character. \\
\noindent\textbf{Hard Points Required:} 2\\
\noindent\textbf{Price:} 350

\subsection{Extra Emitters}
Outfitting a cloaking device with extra emitters makes the cloak even more believable and provides even more protection to the soldier wearing it.\\
\noindent\textbf{Use With:} This attachment can be applied to the cloaking device.\\
\noindent\textbf{Modifiers:} Increase the cloaking device's Defense to 3.\\
\noindent\textbf{Hard Points Required:} 1\\
\noindent\textbf{Price:} 2,000

\subsection{Extra Padding}
This attachment adds a layer of padding to the cloaking device to help absorb the impact of weapons that are not fooled by the illusion.\\
\noindent\textbf{Use With:} This attachment can be applied to the cloaking device.\\
\noindent\textbf{Modifiers:} Increase the cloaking device's soak by +1.\\
\noindent\textbf{Hard Points Required:} 1\\
\noindent\textbf{Price:} 300


\subsection{Stim Injectors}
Stim injectors, or simply 'stims' to those who use them, are used for brief bursts of speed on the battlefield. On command they inject a potent cocktail of adrenaline and various pharmaceuticals that increase speed and reaction time. While it enables characters to get where they're going faster, it does stress the user's system.\\
\noindent\textbf{Use With:} This attachment can be applied to any armor.\\
\noindent\textbf{Modifiers:} Once per round on your turn after you have performed two manoeuvres you may suffer 1 strain to perform the move manoeuvre as an incidental. At the end of any encounter where your character used the stim injectors, they suffer 3 additional strain.\\
\noindent\textbf{Hard Points Required:} 1\\
\noindent\textbf{Price:} 2,500